Human Pose Estimation for Video Game Control

### 2022-05-08 paper/paper.tex
Added a couple of images

@@

To build the first phase of our human-computer interaction device, we use the 
jetson-inference and jetson-utils python packages (\cite{jetsonInference}) 
to build a human pose estimator in Python. The output of this step is a 
collection of 2D keypoints, correpsonding to image coordinates of the locations 
of the 17 body parts detected by PoseNet.

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width = .8\linewidth]{images/flow_chart.png}
    \caption{Data flow within our human-computer interface system. Note 
    the use of a universal pose estimator and game-specific classifiers.}
\end{figure}

@@

To build the first phase of our human-computer interaction device, we use the 
jetson-inference and jetson-utils python packages (\cite{jetsonInference}) 
to build a human pose estimator in Python. The output of this step is a 
collection of 2D keypoints, correpsonding to image coordinates of the locations 
of the 17 body parts detected by PoseNet.\\

\begin{figure}[h]
    \centering
    \includegraphics[width = .8\linewidth]{images/pose_estimations.jpg}
    \caption{An example of the keypoints detected from a frame of video
    by Pose-ResNet-18}
\end{figure}
